\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
conclusions and first part of results

\subsubsection{\zbf vs HTTP}
% TODO: figure out ratio of seeders to leechers
Our next empirical analysis was to keep the ratio of seeders to leechers constant at X, and compare the page load times for a throttled HTTP server vs \zbf as we increase the number of users attempting to concurrently load the page.

@@

% TODO: Katie
\zbf is an open-sourced system
that will allow developers to easily integrate a peer-to-peer CDN to expedite
content delivery to clients even when operating under heavy load.

>>>>

\subsubsection{\zbf vs HTTP}
As seen in fig 1, the performance of \zbf depended on the seeder-to-leecher ratio.
In general, the lowest latency in load time was achieved when the seeder-to-leecher
ratio was highest. However, the system performed well in any condition with many
seeder peers, reflecting the performance benefits provided by chunking of resources
and parallelization of sending chunks. The system performed worst when there were many
leechers and only a few seeders.

% TODO: figure out ratio of seeders to leechers
Our next empirical analysis was to keep the ratio of seeders to leechers constant at X,
and compare the page load times for a throttled HTTP server vs \zbf as we increase the
number of users attempting to concurrently load the page.

@@

\zbf is an open-sourced system that will allow developers to easily utilize
a peer-to-peer CDN to increase the content delivery bandwidth of their sites,
even when operating under heavy request loads. Preliminary data shows that
the system performs well under medium and high workloads, and when the
seeder-to-leecher ratio is high. Future work could refine the system
such that it works well in a wide variety of scenarios. Our results show that peer-to-peer
CDNs are a promising low-cost alternative to CDNs that require on an extensive
network of server and server infrastructure.
